Masterclass Assignment: Real-time Global Illumination

### 2018-01-13 docs/paper.tex
more on documentation

\section{Method}
I used C++ and OpenGL for this assignment, utilising the NCCA Graphics Library NGL \cite{ngl} to interact with OpenGL, and Qt5 to create the user interface. I based my implementation around a demo of the Sponza atrium using NGL\cite{pbrSponza}, that although is quite old, saved me from spending a lot of time writing a grouped Wavefront OBJ and MTL file parser. I extended upon this demo by converting it to use deferred shading, which is necessary for VXGI and other post process effects, using tutorial material from LearnOpenGL\cite{learnDeferred}.

The first step of implementing VXGI was to create a voxelized representation of the albedo and surface normal information in the scene. The method used in the source material\cite{crassinneyretsainzgreeneisemann2011} is explained in great detail in an OpenGL Insights chapter titled \textit{Octree-Based Sparse Voxelization Using the GPU Hardware Rasterizer} \cite{crassingreen2012}, but the basic concept is as followed:
\begin{enumerate}
	\item Generate three projection matrices for orthogonal projections, covering the scene geometry equally, and aligned to each of the coordinate axes.
	\item For each triangle, determine which of the coordinate axes is most aligned with the surface normal, thus generating the maximum number of fragments when transformed using the corresponding projection matrix for that axis.
	\item
\end{enumerate}

@@

\begin{figure}[htbp]\centering
\begin{center}
 \begin{tabular}{|c|c|c|c|}
 \hline
 Voxel Resolution & $256^3$ & $512^3$ & $768^3$ \\
 \hline
 \hline
 Frames per second & 60 & 60 & 60 \\
 \hline
 Memory usage & 1063MiB & 2615MiB & 6628MiB \\
 \hline
 Voxelisation & 2ms & 2ms & 2ms \\
 \hline
 Light Injection & 65ms & 378.5ms & 12294.5ms\\
 \hline
 Shading & 4.5ms & 4.5ms & 4.5ms \\
 \hline
 \end{tabular}
 \caption{Averaged performance results when running with a NVIDIA GTX 1080 8GB at 2560x1080.}
\end{center}
\end{figure}

>>>>

\section{Method}
I used C++ and OpenGL for this assignment, utilising the NCCA Graphics Library NGL \cite{ngl} to interact with OpenGL, and Qt5 to create the user interface. I based my implementation around a demo of the Sponza atrium using NGL \cite{pbrSponza}, that although is quite old, saved me from spending a lot of time writing a grouped Wavefront OBJ and MTL file parser. I extended upon this demo by converting it to use deferred shading, which is necessary for VXGI and other post process effects, using tutorial material from LearnOpenGL \cite{learnDeferred}.

The first step of implementing VXGI was to create a voxelized representation of the albedo and surface normal information in the scene. The method used in the source material \cite{crassinneyretsainzgreeneisemann2011} is explained in great detail in an OpenGL Insights chapter titled \textit{Octree-Based Sparse Voxelization Using the GPU Hardware Rasterizer} \cite{crassingreen2012}, but the basic concept is as followed:
\begin{enumerate}
	\item Generate three projection matrices for orthogonal projections, covering the scene geometry equally, and aligned to each of the coordinate axes.
	\item Draw the scene with depth testing disabled, ensuring fragments are generated for every triangle.
	\item For each triangle, determine which of the coordinate axes is most aligned with the surface normal, thus generating the maximum number of fragments when transformed using the corresponding projection matrix for that axis.
	\item Using either the NVIDIA OpenGL extension \textit{GL CONSERVATIVE RASTERIZATION NV}, or a geometry shader, enlarge each triangle so that fragments are generated regardless of whether it covers a pixels center. This helps to reduce 'cracks' in the voxelisation on surfaces that are angled away from the coordinate axes.
	\item Using the fragment coordinates, depth, and the axis chosen in step 3, infer the texel coordinate that the fragment corresponds to in the target 3D textures. Store the fragment albedo and normal information in 3D textures using a moving average.
\end{enumerate}
Whilst this technique is somewhat easy to explain, I had not previously used the required Image Load/Store commands so I referred to an implementation I found on GitHub \cite{voxelization} to guide me on the OpenGL side of things.

The next step was to inject the scene's emissive values into a 3D texture. This is achieved by raytracing towards the light, for each of the non-transparent texels in the voxelised textures. This is where my implementation differs from the source material \cite{crassinneyretsainzgreeneisemann2011} as I opted to use a dense 3D texture as opposed to a sparse voxel octree. Whilst this was significantly easier to set up, it also severly impacts the speed at which raytracing can be performed through this 3D texture (See Figure~\ref{figure:performance} for performance metrics). The source material \cite{crassinneyretsainzgreeneisemann2011} also details a method for mip-mapping this texture anisotropically along each of the coordinate axes, however I opted to use OpenGL's \lstinline{genMipMaps} method to save time.

The final step was to implement cone tracing in the deferred shading pass. This pass calculates the indirect light contribution, specular lobe contribution, and also soft shadows.

\begin{figure}[htbp]
  \centering
 \subfloat[Specular Cone]{\includegraphics[width=0.45\linewidth]{images/specularCone}}
 \hfill
 \subfloat[Diffuse Indirect Cones]{\includegraphics[width=0.45\linewidth]{images/indirectCones}}
 \caption{A side by side comparison of different render effects is always a good idea to demonstrate a choice of parameters or design of your shader. These were appropriated from \cite{Villegas2016}.}
\end{figure}

@@

\begin{figure}[htbp]\centering
\begin{center}
 \begin{tabular}{|c|c|c|c|}
 \hline
 Voxel Resolution & $256^3$ & $512^3$ & $768^3$ \\
 \hline
 \hline
 Frames per second & 60 & 60 & 60 \\
 \hline
 Memory usage & 1063MiB & 2615MiB & 6628MiB \\
 \hline
 Voxelisation & 2ms & 2ms & 2ms \\
 \hline
 Light Injection & 65ms & 378.5ms & 12294.5ms\\
 \hline
 Shading & 4.5ms & 4.5ms & 4.5ms \\
 \hline
 \end{tabular}
 \caption{\label{figure:performance} Averaged performance results when running with a NVIDIA GTX 1080 8GB at 2560x1080.}
\end{center}
\end{figure}
